### 2023-05-05 main.tex
i
ii

\end{enumerate}
To find the function $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)$ we must fulfil the conditions \eqref{cond1}, \eqref{cond2}, \eqref{cond3}, \eqref{cond4}, \eqref{cond5}, \eqref{cond6}.
% \end{itemize}
\subsubsection{Explicit solution for $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)$}
\begin{equation}
	\begin{split}
		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=&\sum_{i_{1}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+\ldots+i_{(k_{2}+k_{3})}=k_{2}\}}
		\\&
		\prod_{s=1}^{k_{2}+k_{3}}\left\{\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{2}(x)\right\}^{i_{s}}\left\{\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{3}(x)\right\}^{1-i_{s}}
	\end{split}
\end{equation}
We show that it fulfils condition \eqref{cond4}. For the sake of notation we denote by 
\begin{equation}
	\begin{split}
	A_{2}= \left\{\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{2}(x)\right\}\\
	A_{3}=\left\{\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{3}(x)\right\}
	\end{split}
\end{equation}
where the dependence of $A_{2},A_{3}$ on $x$ and $\epsilon$ is understood. 
Therefore we rewrite \eqref{cond4} as 
\begin{equation}
	\begin{split}
		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)
	\end{split}
\end{equation}
The left-hand-side is 
\begin{equation}
		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=\sum_{i_{1}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
\end{equation}
while, on the right-hand-side we have
\begin{equation}
	\begin{split}
A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)&=A_{2}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{2}+i_{k_{2}}+\cdots+i_{(k_{2}+k_{3})}=k_{2}-1\}}\prod_{s=2}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
\\&=
\sum_{i_{1}=1}^{1}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
	\end{split}
\end{equation}
and similarly 
\begin{equation}
	\begin{split}
		A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)&=A_{3}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=2}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
		\\&=
		\sum_{i_{1}=0}^{0}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}.
	\end{split}
\end{equation}
Therefore,
\begin{equation}
	\begin{split}
A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)&=\sum_{i_{1}=1}^{1}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
\\&+
	\sum_{i_{1}=0}^{0}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
	\\&=
	\sum_{i_{1}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
	\\&=
		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)
	\end{split}
\end{equation}
Conditions \eqref{cond1}, \eqref{cond5}, \eqref{cond6} are trivially fulfilled. Conditions \eqref{cond2} and \eqref{cond3} are satisfied because $B_{2}(x),B_{3}(x)$ are rising operators.

@@

We rewrite
\begin{equation}
	\begin{split}
	D_{ii}^{2L-1}&=2e_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}+2(N-1)e_{ii}^{tot}
\end{split}
\end{equation}
then
\begin{equation}
\begin{split}
\boxed{D_{ii}^{2L-1}=	2Ne_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}}
	\end{split}
\end{equation}
{\color{blue} In case of a chain $L=2$ and $N=3$ and choosing $i=2$ this reads as 
\begin{equation*}
	D_{22}^{2L-1}=6e_{22}^{tot}+e_{11}^{tot}-e_{22}^{tot}-e_{33}^{tot}-2e_{22}^{tot}e_{22}^{tot}-2e_{23}^{tot}e_{32}^{tot}
\end{equation*}
where
\begin{equation*}
	e_{ab}^{tot}=e_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes e_{ab}\qquad \forall a,b\in \{1,2,3\}
\end{equation*}
This gives exactly
\begin{equation*}
	D_{22}^{2L-1}=\left(
	\begin{array}{ccccccccc}
		2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
		0 & 2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
		0 & 0 & 0 & 2 & 0 & 0 & 0 & 0 & 0 \\
		0 & 0 & 0 & 0 & -2 & 0 & 0 & 0 & 0 \\
		0 & 0 & 0 & 0 & 0 & 0 & 0 & -2 & 0 \\
		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
		0 & 0 & 0 & 0 & 0 & -2 & 0 & 0 & 0 \\
		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & -2 \\
	\end{array}
	\right)
\end{equation*}
}
\textbf{Observation}: it seems to me that, although not diagonal, the $D_{ii}^{2L-1}$ does not chaing the exitation of the chain since we have $e_{ij}^{tot}e_{ji}^{tot}$!\\
%The following \textit{lower diagonal} elements of $U_{0}(x)$, $\forall i=2,\ldots,L$ and for $j=1$
%\begin{equation}
%	C_{i}(x)=C_{i}^{2L-1}x^{2L-1}+\ldots
%\end{equation}
%where the coefficient is
%\begin{equation}\label{c}
%	C_{i}^{2L-1}=2e_{1i}^{tot}+2\sum_{a< b}\left(e_{1i}^{[a]}e_{11}^{[b]}-e_{1i}^{[a]}e_{ii}^{[b]}-\sum_{a=2\,:\,k\neq j}^{N}e_{1a}^{[a]}e_{ai}^{[b]}\right)
%\end{equation}
Moreover, $\forall j=2,\ldots,L$ and for $i=1$
\begin{equation}
	B_{j}(x)=B_{j}^{2L-1}x^{2L-1}+\ldots
\end{equation}
where the coefficient is 
\begin{equation}\label{b}
\begin{split}
	B_{j}^{2L-1}&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-e_{j1}^{[a]}e_{jj}^{[b]}-\sum_{a=2\,:\,k\neq j}^{N}e_{a1}^{[a]}e_{ja}^{[b]}\right)\\
	&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-\sum_{a=2}^{N}e_{a1}^{[a]}e_{ja}^{[b]}\right)
\end{split}
\end{equation}
then
\begin{equation}
\begin{split}
	\boxed{B_{j}^{2L-1}=2e_{j1}^{tot}+
	2\sum_{a,b=1\,:\, a<b}^{L}e_{j1}^{[a]}e_{11}^{[b]}-2\sum_{a,b=1\,:\, a>b}^{L}\sum_{a=2}^{N}e_{ja}^{[a]}e_{a1}^{[b]}}
\end{split}
\end{equation}
\textbf{Remark}: it is easy to see that, when restricted to the case of 2 species,  \eqref{a2lp},\eqref{a2l},\eqref{a2lm1} correspond to the one compute in \cite{frassek2020eigenstates}. \\ \\
The interesting charges (we only look for the first non trivial one) take the following form

>>>>

\end{enumerate}
To find the function $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)$ we must fulfil the conditions \eqref{cond1}, \eqref{cond2}, \eqref{cond3}, \eqref{cond4}, \eqref{cond5}, \eqref{cond6}.
% \end{itemize}
\subsubsection{Explicit solution for $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)$ using symmetric group}
TO ADD
\subsubsection{Explicit solution for $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)$}
\begin{equation}
	\begin{split}
		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=&\sum_{i_{1}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+\ldots+i_{(k_{2}+k_{3})}=k_{2}\}}
		\\&
		\prod_{s=1}^{k_{2}+k_{3}}\left\{\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{2}(x)\right\}^{i_{s}}\left\{\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{3}(x)\right\}^{1-i_{s}}
	\end{split}
\end{equation}
We show that it fulfils condition \eqref{cond4}. For the sake of notation we denote by 
\begin{equation}
	\begin{split}
	A_{2}= \left\{\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{2}(x)\right\}\\
	A_{3}=\left\{\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{3}(x)\right\}
	\end{split}
\end{equation}
where the dependence of $A_{2},A_{3}$ on $x$ and $\epsilon$ is understood. 
Therefore we rewrite \eqref{cond4} as 
\begin{equation}
	\begin{split}
		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)
	\end{split}
\end{equation}
The left-hand-side is 
\begin{equation}
		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=\sum_{i_{1}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
\end{equation}
while, on the right-hand-side we have
\begin{equation}
	\begin{split}
A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)&=A_{2}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{2}+i_{k_{2}}+\cdots+i_{(k_{2}+k_{3})}=k_{2}-1\}}\prod_{s=2}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
\\&=
\sum_{i_{1}=1}^{1}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
	\end{split}
\end{equation}
and similarly 
\begin{equation}
	\begin{split}
		A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)&=A_{3}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=2}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
		\\&=
		\sum_{i_{1}=0}^{0}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}.
	\end{split}
\end{equation}
Therefore,
\begin{equation}
	\begin{split}
A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)&=\sum_{i_{1}=1}^{1}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
\\&+
	\sum_{i_{1}=0}^{0}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
	\\&=
	\sum_{i_{1}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
	\\&=
		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)
	\end{split}
\end{equation}
Conditions \eqref{cond1}, \eqref{cond5}, \eqref{cond6} are trivially fulfilled. Conditions \eqref{cond2} and \eqref{cond3} are satisfied because $B_{2}(x),B_{3}(x)$ are rising operators.

@@

We rewrite
\begin{equation}
	\begin{split}
	D_{ii}^{2L-1}&=2e_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}+2(N-1)e_{ii}^{tot}
\end{split}
\end{equation}
then
\begin{equation}
\begin{split}
\boxed{D_{ii}^{2L-1}=	2Ne_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}}
	\end{split}
\end{equation}
{\color{blue}ok}
%blue} In case of a chain $L=2$ and $N=3$ and choosing $i=2$ this reads as 
%\begin{equation*}
%	D_{22}^{2L-1}=6e_{22}^{tot}+e_{11}^{tot}-e_{22}^{tot}-e_{33}^{tot}-2e_{22}^{tot}e_{22}^{tot}-2e_{23}^{tot}e_{32}^{tot}
%\end{equation*}
%where
%\begin{equation*}
%	e_{ab}^{tot}=e_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes e_{ab}\qquad \forall a,b\in \{1,2,3\}
%\end{equation*}
%This gives exactly
%\begin{equation*}
%	D_{22}^{2L-1}=\left(
%	\begin{array}{ccccccccc}
%		2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 2 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & -2 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & -2 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & -2 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & -2 \\
%	\end{array}
%	\right)
%\end{equation*}
%}
\textbf{Observation}: it seems to me that, although not diagonal, the $D_{ii}^{2L-1}$ does not chaing the exitation of the chain since we have $e_{ij}^{tot}e_{ji}^{tot}$!\\
%The following \textit{lower diagonal} elements of $U_{0}(x)$, $\forall i=2,\ldots,L$ and for $j=1$
%\begin{equation}
%	C_{i}(x)=C_{i}^{2L-1}x^{2L-1}+\ldots
%\end{equation}
%where the coefficient is
%\begin{equation}\label{c}
%	C_{i}^{2L-1}=2e_{1i}^{tot}+2\sum_{a< b}\left(e_{1i}^{[a]}e_{11}^{[b]}-e_{1i}^{[a]}e_{ii}^{[b]}-\sum_{a=2\,:\,k\neq j}^{N}e_{1a}^{[a]}e_{ai}^{[b]}\right)
%\end{equation}
Moreover, $\forall j=2,\ldots,L$ and for $i=1$
\begin{equation}
	B_{j}(x)=B_{j}^{2L-1}x^{2L-1}+\ldots
\end{equation}
where the coefficient is 
\begin{equation}\label{b}
\begin{split}
	B_{j}^{2L-1}&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-e_{j1}^{[a]}e_{jj}^{[b]}-\sum_{a=2\,:\,k\neq j}^{N}e_{a1}^{[a]}e_{ja}^{[b]}\right)\\
	&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-\sum_{a=2}^{N}e_{a1}^{[a]}e_{ja}^{[b]}\right)
\end{split}
\end{equation}
then
\begin{equation}
\begin{split}
	\boxed{B_{j}^{2L-1}=2e_{j1}^{tot}+
	2\sum_{a,b=1\,:\, a<b}^{L}e_{j1}^{[a]}e_{11}^{[b]}-2\sum_{a,b=1\,:\, a>b}^{L}\sum_{a=2}^{N}e_{ja}^{[a]}e_{a1}^{[b]}}
\end{split}
\end{equation}
\textbf{Remark}: it is easy to see that, when restricted to the case of 2 species,  \eqref{a2lp},\eqref{a2l},\eqref{a2lm1} correspond to the one compute in \cite{frassek2020eigenstates}. \\ \\
The interesting charges (we only look for the first non trivial one) take the following form
